### 2020-08-26 ase20-final/abstract.tex
[ASE20] Final Version approved by IEEE PDF eXpress

To alleviate the problem, we propose \( \tool \), a JavaScript IR-based
Semantics Extraction Toolchain.  It is the first tool that \textit{automatically
synthesizes} parsers and AST-IR translators directly from a given
language specification, ECMAScript.
For syntax, we develop a parser generation technique with \textit{lookahead
parsing} for \( \bnfes \), a variant of the extended BNF used in ECMAScript.
For semantics, \( \tool \) synthesizes AST-IR translators using \textit{forward
compatible} rule-based compilation.  \textit{Compile rules} describe how to
convert each step of abstract algorithms written in a structured natural language
into \( \ires \), an Intermediate Representation that we designed for
ECMAScript.  For the four most recent ECMAScript versions, \( \tool \) automatically
synthesized parsers for all versions, and compiled 95.03\% of the
algorithm steps on average.  After we complete the missing parts manually,
the extracted core semantics of the latest ECMAScript (ES10, 2019) passed all
18,064 applicable tests.  Using this \textit{first formal semantics of modern
JavaScript}, we found nine specification errors in ES10, which were all
confirmed by the Ecma Technical Committee 39.  Furthermore, we showed that \(
\tool \) is \textit{forward compatible} by applying it to nine feature
proposals ready for inclusion in the next ECMAScript, which let us find four
errors in the BigInt proposal.
\end{abstract}

>>>>

To alleviate the problem, we propose \( \tool \), a JavaScript IR-based
Semantics Extraction Toolchain.  It is the first tool that \textit{automatically
synthesizes} parsers and AST-IR translators directly from a given
language specification, ECMAScript.
For syntax, we develop a parser generation technique with \textit{lookahead
parsing} for \( \bnfes \), a variant of the extended BNF used in ECMAScript.
For semantics, \( \tool \) synthesizes AST-IR translators using \textit{forward
compatible} rule-based compilation.  \textit{Compile rules} describe how to
convert each step of abstract algorithms written in a structured natural language
into \( \ires \), an Intermediate Representation that we designed for
ECMAScript.  For the four most recent ECMAScript versions, \( \tool \) automatically
synthesized parsers for all versions, and compiled 95.03\% of the
algorithm steps on average.  After we complete the missing parts manually,
the extracted core semantics of the latest ECMAScript (ES10, 2019) passed all
18,064 applicable tests.  Using this \textit{first formal semantics of modern
JavaScript}, we found nine specification errors in ES10, which were all
confirmed by the Ecma Technical Committee 39.  Furthermore, we showed that \(
\tool \) is \textit{forward compatible} by applying it to nine feature
proposals ready for inclusion in the next ECMAScript, which let us find three
errors in the BigInt proposal.
\end{abstract}

### 2020-08-26 ase20-final/related.tex
[ASE20] Final Version approved by IEEE PDF eXpress

\section{Related Work}\label{sec:related}
Our technique is closely related to three fields: parser generation,
automatic model generation, and formal semantics of JavaScript.

From Packrat parsing~\cite{packrat} with PEG~\cite{peg}, recursive-descent
parsers with backtracking support linear-time parsing.  However, it
has the fundamental problem of ordered choices: \( ab \) is silently
unmatched with \( a ~/~ ab \).  While Generalized LL (GLL) parsing~\cite{gll}
is basically recursive-descent with backtracking that can support general
context-free grammars even in the presence of ambiguous grammars,
its worst-time complexity is \( O(n^3) \) for the input size \( n \) and it
does not support context-sensitive features.  Unlike GLL parsing, our lookahead
parsing is applicable for JavaScript parsers with context sensitive features
such as positive/negative lookaheads. Moreover, the complexity of lookahead
parsing is \( O(k \cdot n) \) for the constant
number of tokens \( k \). We experimentally showed that it can generate parsers
for the most recent four versions of ECMAScript.

The closest work to ours in automatic model generation
is \citet{javadoc}'s, which generates Java code from Javadoc comments
for API functions.  Using NLP techniques and heuristic methods,
it produces candidate code and removes wrong ones
by testing them with actual implementation. Unlike their approach, we
introduce a semi-automatic synthesis using general compile rules that
represent common writing patterns of specifications.  The extracted
semantics by \(\tool\) is also executable, which allows to bridge gaps
between the specification written in a natural language and executable
tests.

>>>>

\section{Related Work}\label{sec:related}
Our technique is closely related to three fields: parser generation,
automatic semantics extraction, and formal semantics of JavaScript.

\textbf{Parser Generation:} From Packrat parsing~\cite{packrat} with
PEG~\cite{peg}, recursive-descent
parsers with backtracking support linear-time parsing.  However, it
has the fundamental problem of ordered choices: \( ab \) is silently
unmatched with \( a ~/~ ab \).  While Generalized LL (GLL) parsing~\cite{gll}
is basically recursive-descent with backtracking that can support general
context-free grammars even in the presence of ambiguous grammars,
its worst-time complexity is \( O(n^3) \) for the input size \( n \) and it
does not support context-sensitive features.  Unlike GLL parsing, our lookahead
parsing is applicable for JavaScript parsers with context sensitive features
such as positive/negative lookaheads. Moreover, the complexity of lookahead
parsing is \( O(k \cdot n) \) for the constant
number of tokens \( k \). We experimentally showed that it can generate parsers
for the most recent four versions of ECMAScript.

\textbf{Automatic Semantics Extraction:} The closest work to ours is the formal
semantics extraction for x86~\cite{extract-x86} and ARM~\cite{extract-arm}.
They utilized complex Natural Language Processing (NLP) and Machine Learning
(ML) to extract formal semantics of small-sized low-level assembly languages.
Another related work is \citet{javadoc}'s automatic model generation, which
generates Java code from Javadoc comments for API functions.  Using NLP techniques
and heuristic methods, it produces candidate code and removes wrong ones
by testing them with actual implementation. Unlike their approach, we
introduce a semi-automatic synthesis using general compile rules that
represent common writing patterns of specifications.  The extracted
semantics by \(\tool\) is also executable, which allows to bridge gaps
between the specification written in a natural language and executable
tests.
